Formalizing the Kolmogorov extension Theorem in Lean

### 2023-09-14 Manuscript/proof_outline.tex
fix: Ionescu-Tulcea is 1 person, not 2

\section{Concluding thoughts}
\label{ss:concl}
{\color{blue} The usability of our contribution must be proved by an
  example: Adding to our general theory, we have implemented the
  example of an infinite product measure. (As an application of
  \leanlinecolor{projectiveLimitWithWeakestHypotheses}, we have to use
  complete and separable extended pseudo-metric spaces, but note that
  an implementation of the Theorem by Ionescu and Tulcea would give
  the same result without these prerequisites.) Here, we can build on
  \leanline{Measure.pi}, which defines a finite product measure.
  Using the same automatically inferred instances, we obtain:}

>>>>

\section{Concluding thoughts}
\label{ss:concl}
{\color{blue} The usability of our contribution must be proved by an
  example: Adding to our general theory, we have implemented the
  example of an infinite product measure. (As an application of
  \leanlinecolor{projectiveLimitWithWeakestHypotheses}, we have to use
  complete and separable extended pseudo-metric spaces, but note that
  an implementation of the Ionescu-Tulcea Theorem would give
  the same result without these prerequisites.) Here, we can build on
  \leanline{Measure.pi}, which defines a finite product measure.
  Using the same automatically inferred instances, we obtain:}
